A free/open-source Kazakh-Tatar machine translation system

### 2013-04-22 paper/paper.tex
some cleaning up of some stuff

Lexical coverage of the system is calculated over freely available corpora of Kazakh and Tatar.
For Kazakh, two years worth of content (2010 and 2012) from Radio Free Europe / Radio Liberty's Kazakh-language service\footnote{\url{http://www.azattyq.org/}}, as well as a recent dump of Wikipedia's articles in Kazakh\footnote{\url{http://kk.wikipedia.org/}; {\smallertt kkwiki-20130408-pages-articles.xml.bz2}} were used.
For Tatar, the Tatar Wikipedia\footnote{\url{http://tt.wikipedia.org/}; {\smallertt ttwiki-20130205-pages-articles.xml.bz2}}, the New Testament in Tatar, and content from Radio Free Europe / Radio Liberty's Tatar-language service \footnote{\url{http://www.azatlyk.org/}} from early 2007 to early 2012.
The versions of the transducers tested were {\tt {\small r43595}} from the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium}}  Corpora were divided into 10 parts each; the coverage numbers given are the averages of the coverage as calculated for each of these parts, and the standard deviation presented is the standard deviation of the coverage on each corpus.

@@

%FIXME: replace old text
As can be seen in Table~\ref{table:coverage}, the coverage for the news corpora approaches
that of a broad-coverage MT system, with one word in ten unknown. These unknown words are 
principally proper nouns. For the Wikipedia corpus, the coverage is substantially worse. This is 
due to \textbf{FIXME: why?}

\begin{table}
	\centering
	\begin{tabular}{llrrr}
		\toprule
		Corpus          & Tokens & Coverage & stdev\\
		\midrule
		RFERL 2010      & 3.2M   & 90.19\% & $\pm$ 0.23\% \\
		RFERL 2012      & 2.9M   & 89.74\% & $\pm$ 0.59\% \\
		Wikipedia       & 1.2M   & 80.75\% & $\pm$ 5.23\% \\
		\bottomrule
	\end{tabular}
	\caption{Naïve trimmed coverage of the Kazakh-Tatar system}
	\label{table:coverage}
\end{table}

>>>>

Lexical coverage of the system is calculated over freely available corpora of Kazakh and Tatar.

For Kazakh, two years worth of content (2010 and 2012) from Radio Free Europe / Radio Liberty's Kazakh-language service,\footnote{\url{http://www.azattyq.org/}} as well as a recent dump of Wikipedia's articles in Kazakh\footnote{\url{http://kk.wikipedia.org/}; {\smallertt kkwiki-20130408-pages-articles.xml.bz2}} were used.

For Tatar, the Tatar Wikipedia,\footnote{\url{http://tt.wikipedia.org/}; {\smallertt ttwiki-20130205-pages-articles.xml.bz2}} the New Testament in Tatar, and content from Radio Free Europe / Radio Liberty's Tatar-language service\footnote{\url{http://www.azatlyk.org/}} from early 2007 to early 2012.
The versions of the transducers tested were {\tt {\small r43595}} from the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium}}  Corpora were divided into 10 parts each; the coverage numbers given are the averages of the coverage as calculated for each of these parts, and the standard deviation presented is the standard deviation of the coverage on each corpus.

@@

As can be seen in table~\ref{table:coverage}, the coverage for the news corpora approaches that of a broad-coverage MT system, with one word in ten unknown.  These unknown words are principally proper nouns.  For the Wikipedia corpus, the coverage is substantially worse.  This is due to the fact that this corpus is ``dirtier'', as well as to the fact that it has contains many more proper nouns.

\begin{table}
	\centering
	\begin{tabular}{llrrr}
		\toprule
		Corpus          & Tokens & Coverage & stdev\\
		\midrule
		RFERL 2010      & 3.2M   & 90.19\% & $\pm$ 0.23\% \\
		RFERL 2012      & 2.9M   & 89.74\% & $\pm$ 0.59\% \\
		Wikipedia       & 1.2M   & 80.75\% & $\pm$ 5.23\% \\
		\bottomrule
	\end{tabular}
	\caption{Naïve trimmed coverage of the Kazakh-Tatar system}
	\label{table:trimmedcoverage}
\end{table}
